Client-Side Indexes for Fast Full-Text Searching

### 2014-12-08 paper/paper.tex
goals

@@

>>>>

In this section, we explain the overall goals and architecture of Lucy.js, how it fits into IndexedDB, as well as give futher details of our implementation.

\subsection{Goals}

The two main goals of Lucy.js we aimed to achieve while implementing it were: (i) to build a search engine extension to IndexedDB that is easy to use and similar to the existing IndexedDB API, and (ii) to create different types of indexes that can all be used for full-text searching and find out which are more suited to which tasks and what the trade-offs are. We design Lucy.js so that it is easy as a developer to be able to specify which type of index to make on a field based on the type of queries that will most often be submitted.

\subsection{IndexedDB}

@@

\subsection{Implementation}

We created Lucy.js in JavaScript, as the IndexedDB API is also in JavaScript.
